Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits

### 2018-11-08 Manuscript_draft/Manuscript_draft.Rmd
ideas

*Keywords*: heterospecific pollen, plant reproduction, fitness, pollen competition

@@

# INTRODUCTION
[Cut and paste some paragraphs from your literature review/ proposal](Romina)

@@

In natural systems plant species normally coexist and share their floral visitors with other species (Bascompte et al., 2003). This pollinator sharing from the plant perpective can be negative due to competition (refs) or positive due to facilitation (refs). Moreover, once the pollinator has landed on the stigma some other issues for the species fitness may arise, the arrival of foreign pollen and conspecific pollen loss (Morales & Traveset 2008)

>>>>

*Keywords*: heterospecific pollen, plant reproduction, fitness, interspecific competition, phylogenetic distance.

@@

# INTRODUCTION

@@

In natural systems plant species normally coexist and share their floral visitors with other species @bascompte2003. This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014. Once, the floral visitor has arrived to the flower, pollen deposition can take place and with an increasing number of visits the higher the chances of ovule fertilization (Refs).

I like what I have so far BUT we can make the story more complete

Moreover, once the pollinator has landed on the stigma some other issues for the plant species may arise, the arrival of foreign pollen and conspecific pollen loss @morales2008.

### 2018-11-08 Manuscript_draft/Manuscript_draft.tex
ideas

\title{Working title, The impact of heterospecific pollen on plant reproductive
success is mediated by phylogenetic distance and floral reproductive
traits}
\author{
Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
true
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Working title, The impact of heterospecific pollen on plant reproductive
success is mediated by phylogenetic distance and floral reproductive
traits
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader \textsuperscript{1,2} 
true
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
\\*
\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
\\*
\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

\emph{Keywords}: heterospecific pollen, plant reproduction, fitness,
competition

@@

\href{Romina}{Cut and paste some paragraphs from your literature review/
proposal}

@@

In natural systems plant species normally coexist and share their floral
visitors with other species (Bascompte et al., 2003). This pollinator
sharing from the plant perpective can be negative due to competition
(refs) or positive due to facilitation (refs). Moreover, once the
pollinator has landed on the stigma some other issues for the species
fitness may arise, the arrival of foreign pollen and conspecific pollen
loss (Morales \& Traveset 2008)

@@

@@

Discuss.

@@

>>>>

\title{Working title, The impact of heterospecific pollen on plant reproductive
success is mediated by phylogenetic distance and floral reproductive
traits}
\author{
Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
Jose
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Working title, The impact of heterospecific pollen on plant reproductive
success is mediated by phylogenetic distance and floral reproductive
traits
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader \textsuperscript{1,2} 
Jose \textsuperscript{*} \textsuperscript{3} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
\\*
\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
\\*
\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

\emph{Keywords}: heterospecific pollen, plant reproduction, fitness,
interspecific competition, phylogenetic distance.

@@

@@

In natural systems plant species normally coexist and share their floral
visitors with other species (Bascompte et al., 2003). This pollinator
sharing from the plant perpective can be negative due to competition
(refs) or positive due to facilitation Carvalheiro et al. (2014).
Moreover, once the pollinator has landed on the stigma some other issues
for the species fitness may arise, the arrival of foreign pollen and
conspecific pollen loss (Morales \& Traveset 2008)

@@

\href{}{comment starts} Glasshouse trial • Species selected and why --
how you made them co-flower • Give details of sources and planting
seeds, growth medium in pots, temperature and light details • Hand
crosses and how you did them, how you measured seed set over time. •
Analyses of data -- standardization, means, matrices etc.

• Analyses and technical difficulties: We calculated effect size by
subtracting the mean of the cross pollinated seed set by the mean effect
of the HP pollen (explain exactly what figures you used to calculate
this) -- check with liam about potentially using missing values analyses
for the species we don't have?

Check that the method is working well to prove that your crosses were
close to 50\% results in SI i.e not all mixes were 50/50\% and we have
now counted all the pollen to make this a quantitative variable. We also
need to factor in the point that we have different total abundances of
pollen across our treatments, irrespective of ratios. To what extent are
differences in the ratios of pollen applied by hand across different
plant families influenced by plant traits such as pollen size,
morphology and stigma surface type?

Results -- may need to include amount of pollen in models as random
factor- prefill matrix with missing value analyse for the species you
don't have.\\
Question 1: how do different pollination treatments (100\% HP, 50\% HP,
self and cross ) impact HP pollen across different plant families? Even
with 100\% HP one (or more species?) still produced seed set.

Result Effect size of Seed set \textasciitilde{} phylogenetic distance
relationship We found that the variation ?/ mean effect size of seed set
is positively related to phylogenetic distance. This means the more
unrelated the species are, the greater the negative impact of
heterospecific pollen (give stats effect size i.e.~Procrustes, X = 0.35;
P = 0.03)

Question 2 : what are the main traits impacting HP impacts?
(compatibility system, pollen size, stigma surface, wet/dry stigma,
length of style etc.

Effect size of seed set \textasciitilde{} floral traits/ reproductive
plant traits We found that the three best terms to explain the variation
in seed set is pollen/ovule ratio, stigma width and style length (Stats
effect size i.e.~X = 0.39, P = 0.02).\\
Need to provide correlation matrix for all traits just for 10 species
Show both ways to present this. Which particular traits do you find
significant effects for? Show this and give stats. Present plot for each
trait and effect size

\href{}{comment finishes}

@@

Discussion

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  What are the implications of the findings?
\end{enumerate}

@@

\hypertarget{ref-carvalheiro2014}{}
Carvalheiro, L. G., J. C. Biesmeijer, G. Benadi, J. Fründ, M. Stang, I.
Bartomeus, C. N. Kaiser-Bunbury, M. Baude, S. I. Gomes, V. Merckx, and
others. 2014. The potential for indirect effects between co-flowering
plants via shared pollinators depends on resource abundance,
accessibility and relatedness. Ecology letters 17:1389--1399.
